Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-05-10 Paper.Rmd
joruney conts vol3

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods @10.2307/1830691. Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop). On the other hand, quality of Experience goods can't be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).

@@

Review Rating (Review Extremity) is another important identifier of perceived helpfulness. This is usually the star rating on a 1-5 or 1-10 scale and resembles the evaluation of the reviewer for a given product. It's effect on perceived helpfulness is rather divergent in the literature. A number of researchers found out that there is a non-linear relationship between review extremity and perceived helpfulness. Specifically, a U-Shaped function which means that reviews that are on the extremes (either very negative or very positive) are more helpful than neutral reviews[ @mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006]. In other studies, linear positive relationship was found. In other words, positively rated reviews are more useful [@pan2011; @schindler2012; @korfiatis2012; @lee2016; @choi2020]. There are also results that support negative linear relationship[@chua2014] and no effect at all[@hong2017].

@@

-   Nelson's two paper as an Economics theory. SEC Classification.

-   Negativity Bias Theory and Loss Aversion

>>>>

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods \@10.2307/1830691. Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop). On the other hand, quality of Experience goods can't be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).

@@

Review Rating (Review Extremity) is another important identifier of perceived helpfulness. This is usually the star rating on a 1-5 or 1-10 scale and resembles the evaluation of the reviewer for a given product. It's effect on perceived helpfulness is rather divergent in the literature. A number of researchers found out that there is a non-linear relationship between review extremity and perceived helpfulness. Specifically, a U-Shaped function which means that reviews that are on the extremes (either very negative or very positive) are more helpful than neutral reviews[@mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006]. In other studies, linear positive relationship was found. In other words, positively rated reviews are more useful [@pan2011; @schindler2012; @korfiatis2012; @lee2016; @choi2020]. There are also results that support negative linear relationship[@chua2014] and no effect at all[@hong2017].

@@

## Search and Experience Goods Classification

-   extend this later and try to connect to the methodology

Nelson (1970) @10.2307/1830691 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981]. Search Attributes are the qualities that can be assessed before purchase. On the contrary, Experience Attributes can only be assessed by using the product itself, in other words evaluation is only possible after purchase. A single good can have both search and experience attributes. Depending on its dominant attributes the good can be classified as Search or Experience. A product's Total Cost consists of both Search Cost and Product Cost. This Search Cost is higher for Experience Goods, in other words, information search is costlier for Experience Goods than Search Goods.

To explain it in a more generalized way, let's also define what "search" is. Nelson (1970) @10.2307/1830691 defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search". People will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search. This is why search is costlier for Experience Goods. For instance, getting information about a car (test drive, guides on the web etc.) is less costly than actually buying it. Even though a car has experience attributes, with this logic it is considered as a search good @klein1998.

-   might explain why negative reviews arent that helpful for movies

## Negativity Bias Theorem and Loss Aversion

-   needs to be connected to the method

Humans tend to care about losses more than same amount of gains. Losing 100\$ is psycholgically much more impactful than finding 100\$. This behavior is best explained by "loss aversion" from Behavioral Economics. [@kahneman1979; @schindler2017]. Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses @herr1991.

Negativity Bias Theorem has four main aspects, namely, higher negative potency -- Negative signals have more impact on people than positive ones. --, steeper negative gradients -- Negativity of negatives events grows faster in space and time than positive ones. --, higher negative dominance --
A combination of equally negative and positive cues results in more negative impressions. --, and various negative differentiations -- Negative cues produce more diverse individual responses than positive ones. --[ @rozin2001; @sen2007; @eslami2018].
